Laura Stoddard VIP Timeline

### 2020-04-27 Markdown Documents/Hypotheses_Rationale.Rmd
moved a bunch of markdown documents

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Testing - What is the best way to replicate a Word comment bubble when editing specific text in document?

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Increasing wildfire severity has further garnered attention for the financial burden it poses to the federal government. The United States spends approximately $1 billion every year to fight wildfires. This however, only approximates the direct costs of wildfire relief. Given that outdoor recreation is significantly affected by wildfire smoke, a secondary goal of this project will be to generate an order of magnitude estimate on National Park Service revenue lost due to increased wildfire smoke.

### 2020-04-27 Markdown Documents/Laura_Stoddard_VIP_Timeline.Rmd
moved a bunch of markdown documents

load("feefit.rda")
SMdat<-read_csv("~/SmokeProject/Data/MergedDataComplete.csv")
FEdat<-read_csv("~/SmokeProject/Data/LauraStoddardEntryFeeCsv.csv")
```

@@

This is what's called an generalized linear model. The "poisson" part just tells the computer that we are modeling values that are discrete counts (1,4,7,etc.)

```{r, eval=FALSE}
feefit<-stan_glm(SingleVisitorEntryFee~Year+Park,family="poisson",data=d,iter=6000)
```

@@

>>>>

load("~/SmokeProject/ModelObjects/feefit.rda")
SMdat<-read_csv("~/SmokeProject/Data/MergedDataComplete.csv")
FEdat<-read_csv("~/SmokeProject/Data/LauraStoddardEntryFeeCsv.csv")
```

@@

This is what's called an generalized linear model. The "Poisson" part just tells the computer that we are modeling values that are discrete counts (1,4,7,etc.)

```{r, eval=FALSE}
feefit<-stan_glm(SingleVisitorEntryFee~Year+Park,family="Poisson",data=d,iter=6000)
```

@@

4/6/2020 Plotting 1
------

We will use the package ggplot2 to plot the data that you have collected/extrapolated.

If you remember from before, the ggplot() function follows the [grammar of graphics](https://towardsdatascience.com/a-comprehensive-guide-to-the-grammar-of-graphics-for-effective-visualization-of-multi-dimensional-1f92b4ed4149), a theory for how to visualize data that relies on stacking layers on top of each other.

When you create ggplot() code, the top most code will be the first layer created. For our purposed, we will always want this to be the axes of the figure. We will do this by specifying the data and the x and y axes. Remember that the x and y axes need to be wrapped in an aestetic function aes(). This just tells ggplot to look for these things in the dataset that we specified.

```{r}
library(ggplot2) #load the package

ggplot(data= d, aes(x=Year,y=SingleVisitorEntryFee))

You'll see that this just "sets the stage" for the rest of the plot. We haven't told it what kind of plot we want yet.

Next, we will layer the data on top of this background.

```{r}
ggplot(data= d, aes(x=as.character(Year),y=SingleVisitorEntryFee))+
  geom_boxplot()
```

Is this the best way to visualize this simple dataset? probably not. Can you think of  better way?

There is a ton of flexibility in ggplot2. See if you can make this plot better.

Once you do that, see if you can plot your data that you created by extrapolating from the fee data we had.

I like to hand draw my plots first so I know what I'm aiming for.

If you want help and inspiration check out the [Cookbook for ggplot](http://www.cookbook-r.com/Graphs/) and the [ggplot gallery](https://www.r-graph-gallery.com/).

4/13/2020 Plotting 2
------
